---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covid19br

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/paternogbc/covid19br.svg?branch=master)](https://travis-ci.org/paternogbc/covid19br)
<!-- badges: end -->

The goal of covid19br is to provided updated information on the number of cases of corona virus for Brasil.

## Installation

You can install the released development version of covid19br from github with:

``` r
install.packages("devtools") 
devtools::install_github(repo = "paternogbc/covid19br")
```

## Help

In `R`, documentation for `covid19br` dataset can be accessed with the
standard `help` command (e.g., `?covid_br_all` and `?covid_br_states`).

For a online description of the dataset, see [reference
page](https://paternogbc.github.io/covid19br/reference/index.html)

## Load the package data

```{r example}
library(covid19br)
## basic example code

head(covid_br_all)
```

What is the trend in the number of corona virus cases for Brasil?

```{r cars}
library(ggplot2)
ggplot(data = covid_br_all, aes(y = confirmed_cases, x = date)) +
  geom_line()
```


Please note that the 'covid19br' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
