---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `covid19br` 

The goal of `covid19br` is to provided updated and historical data on the number of cases of corona virus for Brasil.

The package will be updated every two days including new data from [Ministério da Saúde](https://saude.gov.br/).

## Current trend 

An updated summary of the number of confirmed covid-19 cases in Brazil is presented [here](https://paternogbc.github.io/covid19br/articles/current_trends.html).

> A versão em portugês desta análise se encontra [aqui](https://paternogbc.github.io/covid19br/articles/tendencia_atual.html).

## Installation

You can install the development version of covid19br from github with:

``` r
install.packages("devtools") 
devtools::install_github(repo = "paternogbc/covid19br")
```

## Help

In `R`, documentation for `covid19br` dataset can be accessed with the
standard `help` command (e.g., `?covid_br_all` and `?covid_br_states`).

For a online description of the dataset, see [reference
page](https://paternogbc.github.io/covid19br/reference/index.html)

## Load the package data

```{r example}
library(covid19br)

# To get historical data for Brazil: 
head(covid_br_all)

# TO get historical data by state:
head(covid_br_states)
```


Please note that the 'covid19br' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
