---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `covid19br` 

The goal of `covid19br` is to provide a permanent repository with data and the entire history of corona virus cases in Brazil.

The package will be updated daily, including new data from the Ministry of Health(https://saude.gov.br/) made available through the platform [IVIS](http://platform.saude.gov.br/novocoronavirus/).

See the package page for [reference](https://paternogbc.github.io/covid19br/index.html).

## Current trend 

An updated summary of the number of confirmed covid-19 cases in Brazil is presented [here](https://paternogbc.github.io/covid19br/articles/en_current_trends.html).

## Installation

You can install the development version of covid19br from github with:

``` r
install.packages("devtools") 
devtools::install_github(repo = "paternogbc/covid19br")
```

## Help

In `R`, documentation for `covid19br` dataset can be accessed with the
standard `help` command (e.g., `?covid_br_all` and `?covid_br_states`).

For a online description of the dataset, see [reference
page](https://paternogbc.github.io/covid19br/reference/index.html)

## Load the package data

```{r example}
library(covid19br)

# To get historical data for Brazil: 
head(covid_br)

# TO get historical data by state:
head(covid_states)

# TO get historical data by region:
head(covid_regions)
```

## Raw data

The raw data are downloaded via the package [`coronabr`](https://github.com/paternogbc/coronabr)^[Package developed by [Andrea](https://twitter.com/SanchezTapiaA) and [Sara](https://twitter.com/mortarasara)] which provides an excellent function to download the raw data directly from the platform [IVIS](http://platform.saude.gov.br/novocoronavirus/) of the Ministry of Health.

***

Please note that the 'covid19br' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
